### 2014-05-02 Article.tex
Create Article.tex

\documentclass[11pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}

\usepackage{comment}

\newcommand{\prog}[1]{{\tt#1}}
\newcommand{\underscore}{$\_\,$}

\begin{document}

\end{document}

### 2014-05-02 Article.tex
Update Article.tex

@@
 
+\section{Abstract}
+In this contribution, we investigate the problem of "SwitchBoxes".
+The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes", that swap two wires. We tried to minimize the number of boxes that were necessary.
+We introduce a conjecture that puts our problem in relation with binary insertion sort. We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.
+
+\section{Introduction}
+
 \end{document}

### 2014-05-02 Article.tex
Article Abstract + Intro 02/05 16h00

@@
 \usepackage{listings}
+\usepackage{amssymb}
+\usepackage{amsmath}
 
@@
 In this contribution, we investigate the problem of "SwitchBoxes".
-The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes", that swap two wires. We tried to minimize the number of boxes that were necessary.
-We introduce a conjecture that puts our problem in relation with binary insertion sort. We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.
+The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes",
+ that swap two wires. We tried to minimize the number of boxes that were necessary.
+We introduce a conjecture that puts our problem in relation with binary insertion sort. 
+We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.
 
 \section{Introduction}
+The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from the top), 
+we try to generate all the permutations of these wires by using boxes. 
+A box takes two wires, and is allowed to swap these wires. We can concatenate these boxes to get a configuration of boxes.
+The configuration is said valid if, by swapping or not the wires on every box, we can obtain any permutation of the $n$ wires.
+
+Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0 or 1.
+A configuration of boxes C is the concatenation of k boxes $\tau_1, \ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) = \tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.
+The configuration C is said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
+
+Given this problem, we tried to determine the best lower bound of the number of boxes $k$.
+
+We can easily determine trivial lower and upper bounds of the number of boxes~:\\
+Given the fact that C is an application, we need to have $Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$ has to be greater than $\log_2(n!)$.\\
+We also have an upper bound~:
+The traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We obtain that the optimal k is smaller than $\frac{(n-1)(n-2)}{2}$.
+
+In this contribution, we first develop how the optimal k seems to be linked to the maximal number of comparisons for sorting n elements by binary insertion.
+We explain why we guess that those numbers are equal.
+
+In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
+for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.
+
+In addition, we give some ideas we tried to develop in order to prove mathematically this conjecture.
+
+In the rest of this paper, $opt_n$ will be the optimal number of boxes for $n$ wires.
 

### 2014-05-02 Article.tex
Article Abstract+Intro+Conjecture

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{url}
 
 \usepackage{comment}
+
+\newtheorem*{Conj*}{Conjecture}
 
@@
 
-In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
+In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
 for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.
@@
 
+% Part 0. Introduction
+% Part 1. Conjecture
+% Part 2. Optimisation
+% Part 3. Pistes de recherche
+
+\section{Our conjecture}
+
+To understand the problem, we first tried manually to get $opt_n$ for very small values of $n$.\\
+For $n=2$, the answer is quite simple~: One box is enough and necessary to swap the two wires.\\
+For $n=3$, two boxes aren't enough. Using a permutation, we can consider that the first box swap the wires 1 and 2, and that the second box swap the wires 2 and 3.
+Then the permutation $(1,3)$ can't be generated with this configuration. Hence, we have $opt_3=3$.
+
+For greater values of $n$, we implemented a naive and brutal algorithm that for $k$ given, creates all the possible configurations of $k$ boxes, 
+and checks if one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,  we increment $k$ and try again until we get a valid configuration.
+With this algorithm, we easily get $opt_n$.\\
+However, this only works for small values of $n$. For $n$ greater than 6, we lack memory and time to achieve the computation.
+
+Using this algorithm, we got the following results~:
+
+\begin{tabular}{|c|c|}
+\hline
+Number of wires $n$ & $opt_n$ \\
+\hline
+2 & 1 \\
+3 & 3 \\
+4 & 5 \\
+5 & 8 \\
+6 & 11 \\
+\hline
+\end{tabular}\\
+
+According to the fact that this sequence is exactly the beginning of the sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line Encyclopedia of Integer Sequences, Sorting numbers: maximal number of comparisons for sorting n elements by binary insertion, \url{http://oeis.org/A001855}},
+corresponding to the maximal number of comparisons for sorting $n$ elements by binary insertion, we guessed that these sequences were equal.
+
+\Large
+\begin{Conj*}
+$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements by binary insertion.
+\end{Conj*}
+\normalsize
+
+In order to prove this conjecture for greater values, we tried to optimize our checking algorithm. That will be described in the next part.
+
+\section{Hypothesis box system}
+
+\subsection{The basis set}
+
+\subsection{Truncation}
+
+\subsection{Testing the box system}
+
+\subsection{Useless box elimination}
+
 \end{document}

### 2014-05-02 Article.tex
Add stuff

--- 2014-05-02 Article.tex
@@
 \section{Abstract}
-In this contribution, we investigate the problem of "SwitchBoxes".
-The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes",
- that swap two wires. We tried to minimize the number of boxes that were necessary.
-We introduce a conjecture that puts our problem in relation with binary insertion sort. 
-We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.
+
+In this contribution, we investigate the problem of "SwitchBoxes".  The goal is,
+given $n$ wires, to generate all the permutations of these wires by using
+"boxes", that swap two wires. We tried to minimize the number of boxes that were
+necessary.  We introduce a conjecture that puts our problem in relation with
+binary insertion sort.  We successfully used a heavily optimized algorithm to
+prove this conjecture for small values of $n$.
 
 \section{Introduction}
-The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from the top), 
-we try to generate all the permutations of these wires by using boxes. 
-A box takes two wires, and is allowed to swap these wires. We can concatenate these boxes to get a configuration of boxes.
-The configuration is said valid if, by swapping or not the wires on every box, we can obtain any permutation of the $n$ wires.
 
-Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0 or 1.
-A configuration of boxes C is the concatenation of k boxes $\tau_1, \ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) = \tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.
-The configuration C is said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
+The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from
+the top), we try to generate all the permutations of these wires by using boxes.
+A box takes two wires, and is allowed to swap these wires. We can concatenate
+these boxes to get a configuration of boxes.  The configuration is said valid
+if, by swapping or not the wires on every box, we can obtain any permutation of
+	the $n$ wires.
 
-Given this problem, we tried to determine the best lower bound of the number of boxes $k$.
+Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a
+permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0
+or 1.  A configuration of boxes C is the concatenation of k boxes $\tau_1,
+\ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) =
+\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration C is
+said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
 
-We can easily determine trivial lower and upper bounds of the number of boxes~:\\
-Given the fact that C is an application, we need to have $Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$ has to be greater than $\log_2(n!)$.\\
-We also have an upper bound~:
-The traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We obtain that the optimal k is smaller than $\frac{(n-1)(n-2)}{2}$.
+Given this problem, we tried to determine the best lower bound of the number of
+boxes $k$.
 
-In this contribution, we first develop how the optimal k seems to be linked to the maximal number of comparisons for sorting n elements by binary insertion.
+We can easily determine trivial lower and upper bounds of the number of
+boxes~:\\ Given the fact that C is an application, we need to have
+$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$
+has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
+traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We
+obtain that the optimal k is smaller than $\frac{(n-1)(n-2)}{2}$.
+
+In this contribution, we first develop how the optimal k seems to be linked to
+the maximal number of comparisons for sorting n elements by binary insertion.
 We explain why we guess that those numbers are equal.
 
-In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
-for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.
+In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and
+how we demonstrated that the number of comparisons is an upper bound of the
+optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
+algorithm and by constructing a precise configuration.
 
-In addition, we give some ideas we tried to develop in order to prove mathematically this conjecture.
+In addition, we give some ideas we tried to develop in order to prove
+mathematically this conjecture.
 
-In the rest of this paper, $opt_n$ will be the optimal number of boxes for $n$ wires.
+In the rest of this paper, $opt_n$ will be the optimal number of boxes for $n$
+wires.
+
+% Part 0. Introduction
+% Part 1. Conjecture
+% Part 2. Optimisation
+% Part 3. Pistes de recherche
+
+\section{Our conjecture}
+
+\subsection{First examples}
+
+$n=2$ : $S_2(e_1) = (1,2)^{e_1}$
+
+$n=3$ : $S_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$
+
+$n=4$ : fill in later
+
+\subsection {Notation}
+
+We abbreviate the previous notation in the following way :
+
+$$S_2 = (1,2)$$
+
+$$S_3 = (1,2)(2,3)(1,2)$$
+
+$$S_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$
+
+\section{Hypothesis box system}
+
+We have found a box system that seems to generate all permutations for all $n$.
+We have managed to prove that this box system is valid for small values of $n$
+($n \leq 13$), and have found that the box systems were still valid when some
+boxes were removed.
+
+\subsection{The basis box configuration}
+
+We first define the $q$-block at position $i$ by :
+
+$$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1)(q+2*2^i-1)$$
+
+For example: 
+$$B(0,i) = (i,i+1)$$
+$$B(1,i) = (i, i+2)(i+1, i+3)$$
+$$B(2, i) = (i,i+4)(i+1,i+5)(i+2,i+6)(i+3,i+7)$$
+
+Then, for $n=2^p$ we define for $q < p$ the $(p,q)$-line by :
+
+$$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$$
+
+For example:
+$$L(3,0) = (0,1)(2,3)(4,5)(6,7)$$
+$$L(3,1) = (0,2)(1,3)(4,6)(5,7)$$
+$$L(3,2) = (0,4)(1,5)(2,6)(3,7)$$
+
+We now conjecture that the following configuration generates all permutations
+for $n=2^p$ :
+
+$$S_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$
+
+For example :
+
+$$
+\begin{aligned}
+	S_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
+        & = & (0,1)(2,3)(4,5)(6,7) \\
+		& & (0,2)(1,3)(4,6)(5,7) \\
+		& & (0,4)(1,5)(2,6)(3,7) \\
+		& & (0,2)(1,3)(4,6)(5,7) \\
+        & & (0,1)(2,3)(4,5)(6,7)
+\end{aligned}$$
+
+\subsection{Truncation}
+
+For $n$ which is not a power of two, we construct $S_n^0$ by taking
+$S_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.
+
+For example, $S_5^0$ can be generated from $S_8^0$ and by removing quite a lot
+of the boxes. We obtain the following solution :
+
+$$S_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$
+
+\subsection{Testing the box system}
+
+\subsection{Useless box elimination}
 

### 2014-05-02 Article.tex

@@
 
-In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and
-how we demonstrated that the number of comparisons is an upper bound of the
-optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
-algorithm and by constructing a precise configuration.
+In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
+for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.
 
@@
 \section{Our conjecture}
+
+To understand the problem, we first tried manually to get $opt_n$ for very small values of $n$.\\
+For $n=2$, the answer is quite simple~: One box is enough and necessary to swap the two wires.\\
+For $n=3$, two boxes aren't enough. Using a permutation, we can consider that the first box swap the wires 1 and 2, and that the second box swap the wires 2 and 3.
+Then the permutation $(1,3)$ can't be generated with this configuration. Hence, we have $opt_3=3$.
+
+For greater values of $n$, we implemented a naive and brutal algorithm that for $k$ given, creates all the possible configurations of $k$ boxes, 
+and checks if one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,  we increment $k$ and try again until we get a valid configuration.
+With this algorithm, we easily get $opt_n$.\\
+However, this only works for small values of $n$. For $n$ greater than 6, we lack memory and time to achieve the computation.
+
+Using this algorithm, we got the following results~:
+
+\begin{tabular}{|c|c|}
+\hline
+Number of wires $n$ & $opt_n$ \\
+\hline
+2 & 1 \\
+3 & 3 \\
+4 & 5 \\
+5 & 8 \\
+6 & 11 \\
+\hline
+\end{tabular}\\
+
+According to the fact that this sequence is exactly the beginning of the sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line Encyclopedia of Integer Sequences, Sorting numbers: maximal number of comparisons for sorting n elements by binary insertion, \url{http://oeis.org/A001855}},
+corresponding to the maximal number of comparisons for sorting $n$ elements by binary insertion, we guessed that these sequences were equal.
+
+\Large
+\begin{Conj*}
+$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements by binary insertion.
+\end{Conj*}
+\normalsize
+
+In order to prove this conjecture for greater values, we tried to optimize our checking algorithm. That will be described in the next part.
 

### 2014-05-09 Article.tex

@@
 
-\section{Abstract}
+\title{Paper without a name}
+\author{A. Auvolat \and A. Fromherz \and N. Jeannerod}
+\date{June 01, 2014}
+\maketitle
+
+\begin{abstract}
 
@@
 prove this conjecture for small values of $n$.
+
+\end{abstract}
 
@@
 
-In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
-for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.
+In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and
+how we demonstrated that the number of comparisons is an upper bound of the
+optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
+algorithm and by constructing a precise configuration.
 
@@
 
-To understand the problem, we first tried manually to get $opt_n$ for very small values of $n$.\\
-For $n=2$, the answer is quite simple~: One box is enough and necessary to swap the two wires.\\
-For $n=3$, two boxes aren't enough. Using a permutation, we can consider that the first box swap the wires 1 and 2, and that the second box swap the wires 2 and 3.
-Then the permutation $(1,3)$ can't be generated with this configuration. Hence, we have $opt_3=3$.
+To understand the problem, we first tried manually to get $opt_n$ for very small
+values of $n$.\\
+For $n=2$, the answer is quite simple~: One box is enough and necessary to swap
+the two wires.\\
+For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
+the first box swap the wires 1 and 2, and that the second box swap the wires 2
+and 3.  Then the permutation $(1,3)$ can't be generated with this configuration.
+Hence, we have $opt_3=3$.
 
-For greater values of $n$, we implemented a naive and brutal algorithm that for $k$ given, creates all the possible configurations of $k$ boxes, 
-and checks if one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,  we increment $k$ and try again until we get a valid configuration.
-With this algorithm, we easily get $opt_n$.\\
-However, this only works for small values of $n$. For $n$ greater than 6, we lack memory and time to achieve the computation.
+For greater values of $n$, we implemented a naive and brutal algorithm that for
+$k$ given, creates all the possible configurations of $k$ boxes, and checks if
+one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,
+we increment $k$ and try again until we get a valid configuration.  With this
+algorithm, we easily get $opt_n$.\\
+However, this only works for small values of $n$. For $n$ greater than 6, we
+lack memory and time to achieve the computation.
 
@@
 
-According to the fact that this sequence is exactly the beginning of the sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line Encyclopedia of Integer Sequences, Sorting numbers: maximal number of comparisons for sorting n elements by binary insertion, \url{http://oeis.org/A001855}},
-corresponding to the maximal number of comparisons for sorting $n$ elements by binary insertion, we guessed that these sequences were equal.
+According to the fact that this sequence is exactly the beginning of the
+sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line
+Encyclopedia of Integer Sequences, Sorting numbers: maximal number of
+comparisons for sorting n elements by binary insertion,
+\url{http://oeis.org/A001855}}, corresponding to the maximal number of
+comparisons for sorting $n$ elements by binary insertion, we guessed that these
+sequences were equal.
 
@@
 \begin{Conj*}
-$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements by binary insertion.
+$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements
+by binary insertion.
 \end{Conj*}
@@
 
-In order to prove this conjecture for greater values, we tried to optimize our checking algorithm. That will be described in the next part.
+In order to prove this conjecture for greater values, we tried to optimize our
+checking algorithm. That will be described in the next part.
 

### 2014-05-09 Article.tex
Include SVG
add pdf_tex files
Dynamic generation of pdf_tex files
Stuff.

@@
 \usepackage{url}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+
+\newcommand{\includesvg}[1]{%
+  \input{#1.pdf_tex}%
+}
+
+\graphicspath{{svg/}}
 
@@
 
-\title{Paper without a name}
-\author{A. Auvolat \and A. Fromherz \and N. Jeannerod}
+\title{ Paper without a name }
+\author{A. Auvolat \and A. Fromherz \and N. Jeannerod }
 \date{June 01, 2014}
@@
 
-In this contribution, we investigate the problem of "SwitchBoxes".  The goal is,
+In this contribution, we investigate the problem of ``SwitchBoxes''.  The goal is,
 given $n$ wires, to generate all the permutations of these wires by using
-"boxes", that swap two wires. We tried to minimize the number of boxes that were
+``boxes'', that swap two wires. We tried to minimize the number of boxes that were
 necessary.  We introduce a conjecture that puts our problem in relation with
@@
 % Part 3. Pistes de recherche
+
+\begin{figure}
+ \centering
+ \begin{minipage}{.5\textwidth}
+ 	\centering
+	 \def\svgwidth{0.2\textwidth}
+	 \includesvg{svg/2wires_box}
+	 \caption{Trivial solution for 2 wires}
+ \end{minipage}%
+ \begin{minipage}{.5\textwidth}
+ 	\centering
+	 \def\svgwidth{0.5\textwidth}
+	 \includesvg{svg/4wires_box}
+	 \caption{Simple non-optimal solution for 4 wires}
+ \end{minipage}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\def\svgwidth{0.6\textwidth}
+	\includesvg{svg/8wires_box}
+	\caption{Simple non-optimal solution for 8 wires}
+\end{figure}
 

### 2014-05-09 Article.tex
Article.tex modifié

--- 2014-05-09 Article.tex
@@
 the two wires.\\
+
+\begin{figure}
+ \centering
+ \vspace{+20pt}
+ \def\svgwidth{0.15\textwidth}
+ \includesvg{svg/2wires_box}
+ \caption{Optimal configuration for 2 wires}
+\end{figure}
+
 For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
@@
 Hence, we have $opt_3=3$.
+
+\begin{figure}
+ \centering
+ \vspace{+20pt}
+ \def\svgwidth{0.25\textwidth}
+ \includesvg{svg/4wires_box}
+ \caption{Valid, but not optimal configuration for 4 wires}
+\end{figure}
+
+On these representations, a box is a horizontal line that can swap the wires the points are on.
 

### 2014-05-09 Article.tex
haha

--- 2014-05-09 Article.tex
@@
 
-\begin{figure}
- \centering
- \begin{minipage}{.5\textwidth}
- 	\centering
-	 \def\svgwidth{0.2\textwidth}
-	 \includesvg{svg/2wires_box}
-	 \caption{Trivial solution for 2 wires}
- \end{minipage}%
- \begin{minipage}{.5\textwidth}
- 	\centering
-	 \def\svgwidth{0.5\textwidth}
-	 \includesvg{svg/4wires_box}
-	 \caption{Simple non-optimal solution for 4 wires}
- \end{minipage}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\def\svgwidth{0.6\textwidth}
-	\includesvg{svg/8wires_box}
-	\caption{Simple non-optimal solution for 8 wires}
-\end{figure}
-
 \section{Our conjecture}
@@
 the two wires.\\
+
+\begin{figure}
+ \centering
+ \begin{minipage}{.5\textwidth}
+ 	\centering
+	 \def\svgwidth{0.3\textwidth}
+	 \includesvg{svg/boxsys-2-1}
+	 \caption{Trivial solution for 2 wires}
+ \end{minipage}%
+ \begin{minipage}{.5\textwidth}
+ 	\centering
+	 \def\svgwidth{0.5\textwidth}
+	 \includesvg{svg/boxsys-4-6}
+	 \caption{Simple non-optimal solution for 4 wires}
+ \end{minipage}
+\end{figure}
+
 For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
@@
 Hence, we have $opt_3=3$.
+
+\begin{figure}
+	\centering
+	\def\svgwidth{0.7\textwidth}
+	\includesvg{svg/boxsys-8-20}
+	\caption{Simple non-optimal solution for 8 wires}
+\end{figure}
+
+On these representations, a box is a horizontal line that can swap the wires the points are on.
 
@@
 
+\begin{figure}
+	\centering
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\def\svgwidth{0.7\textwidth}
+		\includesvg{svg/boxsys-5-9}
+		\caption{Solution for 5 wires}
+	\end{minipage}%
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\def\svgwidth{0.85\textwidth}
+		\includesvg{svg/boxsys-6-12}
+		\caption{Solution for 6 wires}
+	\end{minipage}
+\end{figure}
+
 \subsection{Testing the box system}

### 2014-05-09 Article.tex
Changes.
Article.tex modifié

@@
 
+\section{Conclusion}
+
+All these results seem to confirm our intuition.
+To go further, we unsuccessfully tried to find applications from the set of trees representing a sort by binary insertion to the set of valid configurations of boxes 
+that would be either one to one or onto, in order to find an inequality between these two sequences of integers.
+We also tried to put our construction of configurations in relation with binary insertion sort.
+
 \end{document}

### 2014-05-23 Article.tex
Changes...

@@
 \usepackage{subcaption}
+\usepackage{mathtools}
 
@@
 \graphicspath{{svg/}}
+
+\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
 
@@
 permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0
-or 1.  A configuration of boxes C is the concatenation of k boxes $\tau_1,
+or 1.  A configuration of boxes $C$ is the concatenation of $k$ boxes $\tau_1,
 \ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) =
-\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration C is
+\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration $C$ is
 said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
@@
 We can easily determine trivial lower and upper bounds of the number of
-boxes~:\\ Given the fact that C is an application, we need to have
+boxes~:\\ Given the fact that $C$ is an application, we need to have
 $Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$
@@
 traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We
-obtain that the optimal k is smaller than $\frac{(n-1)(n-2)}{2}$.
+obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.
 
-In this contribution, we first develop how the optimal k seems to be linked to
-the maximal number of comparisons for sorting n elements by binary insertion.
-We explain why we guess that those numbers are equal.
+In this contribution, we first recall how the sequence of the maximal number of
+comparisons for sorting $n$ elements by binary insertion is defined and develop
+how the optimal $k$ seems to be linked to it.  We then explain why we guess that
+those numbers are equal.
 
@@
 
-% Part 0. Introduction
-% Part 1. Conjecture
-% Part 2. Optimisation
-% Part 3. Pistes de recherche
+\section{The A001855 sequence}
+
+In this paragraph, we will develop on the A001855 sequence, here denoted $u_n$,
+which seems to be in relation with our problem.
+
+$u_n$ is defined as the maximal number of comparisons done by a binary
+insertion sort running on a table of $n$ items.
+
+\begin{verbatim}
+
+    function FindPos(n, T, begin, end)   // find n in T(begin, begin+1, ..., end-1)
+        assert(begin < end)
+        if begin + 1 = end then
+            return begin
+        else
+            mid = E[(begin + end) / 2]
+            if T[mid] > n then
+                return FindPos(n, T, begin, mid)
+            else
+                return FindPos(n, T, mid+1, end)
+
+    function Sort(T)
+        n = T.size
+        S = [T[0]]
+        for i = 1 to n-1
+            pos = FindPos(T[i], S, 0, S.size)
+            insert T[i] in S at position pos
+        return S
+
+\end{verbatim}
+
+This algorithm progressively builds $S$, the table of the elements of $T$ in
+increasing order. This is done by progressively inserting the elements of $T$ in
+$S$ at a position calculated by the $FindPos$ function. The $FindPos$ function
+is based on a binary search, therefore does $O(log(S.size))$ comparisons.
+
+The $u_n$ suite is defined as follows :
+
+$$u_1 = 0$$
+$$\forall n \in \mathbb{N}^*, u_{n+1} = u_n + \ceil{log_2(n)}$$
+
+This sequence is described on the OEIS\footnote{Online Encyclopedia of Integer
+Sequence}, and is referenced under the name A001855.
 
@@
 
-Using this algorithm, we got the following results~:
+Using this algorithm, we got the results in the table of figure~\ref{box-count}.
 
+\begin{figure}
+    \centering
     \begin{tabular}{|c|c|}
@@
     \hline
-\end{tabular}\\
+    \end{tabular}
+    \caption{Minimum box count for small number of wires}
+    \label{box-count}
+\end{figure}
 
-According to the fact that this sequence is exactly the beginning of the
-sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line
-Encyclopedia of Integer Sequences, Sorting numbers: maximal number of
-comparisons for sorting n elements by binary insertion,
-\url{http://oeis.org/A001855}}, corresponding to the maximal number of
-comparisons for sorting $n$ elements by binary insertion, we guessed that these
-sequences were equal.
+According to the fact that this sequence is exactly the beginning of the $u_n$
+sequence described in the previous paragraph, our conjecture is that the
+sequences are equal.
 
@@
 
-$n=4$ : fill in later
+$n=4$ : $S_4(e_1,e_2,e_3,e_4,e_5) = (1, 2)^{e_1} \circ (3,4)^{e_2} \circ
+(1,3)^{e_3} \circ (2, 4)^{e_4} \circ (1,2)^{e_5}$
 
@@
 
+For a box system $S = b_1 b_2 \dots b_p$, we construct the sets :
+
+$$Perm_0 = { id }$$
+$$Perm_k = (b_1 b_2 \dots b_k)(\left\{0,1\right\}^k)$$
+
+The permutation set $Perm_p$ therefore contains all the possible permutations we
+can generate with the $p$ boxes. If $Perm_p = \mathfrak{S}_n$ then the box system
+is valid.
+
+Each set $Perm_k$ is represented in memory as a bitset containing $n!$ bits, one
+for each permutation of $\mathfrak{S}_n$. The isomorphism between the
+permutations of $\mathfrak{S}_n$ and the numbers $\left\{0,1,\dots,n!-1\right\}$ is
+constructed using the standard method described in (a citation).
+
+The representation as a bitset is the most compact representation we have found.
+
 \subsection{Useless box elimination}
+
+We can easily detect that $Perm_{k+1} = Perm_k$ when $ \# Perm_{k+1} = \# Perm_k$,
+because $Perm_k \subset Perm_{k+1}$. When this condition is fulfilled, then we
+know that the box $b_{k+1}$ is useless because it adds no permutation to the set
+of generated permutations. We can therefore remove it from the box system.
+
+By removing the boxes that this method detects as useless from the box system we
+constructed in the previous paragraphs, we have constructed box systems that
+generate all the permutations for $n \leq 13$ and that have $u_n$ boxes (ie the
+conjectured optimum). We have not managed to run the test for $n \geq 14$,
+because the required RAM exceeds 20Go, which is not a resource we have in our
+possession.
 

### 2014-05-30 Article.tex
Changes..
Changes.

@@
 \usepackage{mathtools}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
 
@@
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
+\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
 
@@
 
-The SwitchBoxes problem is a combinatory problem. Given $n$ wires, (coming from
-the top), we try to generate all the permutations of these wires by using boxes.
-A box takes two wires, and is allowed to swap these wires. We can concatenate
-these boxes to get a configuration of boxes.  The configuration is said valid
-if, by swapping or not the wires on every box, we can obtain any permutation of
-    the $n$ wires.
+The SwitchBoxes problem is a combinatory problem. Given $n$ wires, we try to
+generate all the permutations of these wires by using boxes.  A box takes two
+wires and a control bit, and swaps the two entry wires iff the control bit is
+set. We can concatenate these boxes to get a configuration of boxes.  The
+configuration is said valid if, by giving the set of boxes different
+configurations (ie. swapping or not the wires on every box), we can obtain any
+permutation of the $n$ wires.
 
 Mathematically, we consider that the wires are numbers from 1 to $n$. A box is a
-permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ is equal to 0
-or 1.  A configuration of boxes $C$ is the concatenation of $k$ boxes $\tau_1,
-\ldots, \tau_k$, that means, $C(\epsilon_1, \ldots, \epsilon_k) =
-\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration $C$ is
-said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
+permutation $\tau(\epsilon) = (i,j)^{\epsilon}$, where $\epsilon$ represents the
+control bit for the box and is either 0 or 1.  A configuration of boxes $C$ is
+the concatenation of $k$ boxes $\tau_1, \ldots, \tau_k$, that means,
+$C(\epsilon_1, \ldots, \epsilon_k) =
+\tau_1^{\epsilon_1}\circ\ldots\circ\tau_k^{\epsilon_k}$.  The configuration $C$
+is said valid if $C(\{0,1\}^k)= \mathfrak{S}_n$.
 
 Given this problem, we tried to determine the best lower bound of the number of
-boxes $k$.
+boxes $k$ which is valid for $\mathfrak{S}_n$, ie generates all the permutations of $n$
+wires.
 
@@
 boxes~:\\ Given the fact that $C$ is an application, we need to have
-$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediateley obtain that $k$
+$Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediately obtain that $k$
 has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
-traditionnal bubblesort is a valid configuration of the SwitchBoxes problem. We
+traditional bubblesort gives a valid configuration of the SwitchBoxes problem. We
 obtain that the optimal $k$ is smaller than $\frac{(n-1)(n-2)}{2}$.
@@
 
-\begin{verbatim}
-
-    function FindPos(n, T, begin, end)   // find n in T(begin, begin+1, ..., end-1)
-        assert(begin < end)
-        if begin + 1 = end then
-            return begin
-        else
-            mid = E[(begin + end) / 2]
-            if T[mid] > n then
-                return FindPos(n, T, begin, mid)
-            else
-                return FindPos(n, T, mid+1, end)
-
-    function Sort(T)
-        n = T.size
-        S = [T[0]]
-        for i = 1 to n-1
-            pos = FindPos(T[i], S, 0, S.size)
-            insert T[i] in S at position pos
-        return S
-
-\end{verbatim}
+\begin{algorithm}
+\begin{algorithmic}
+\Function{FindPos}{$n, T, b, e$}
+	\Comment{Find $n$ in $T[b, b+1, \dots, e-1]$}
+	\State \textbf{assert} $b < e$
+	\If {$b + 1 = e$}
+		\State \Return $b$
+	\Else
+		\State $m \gets \floor{(b+e)/2}$
+		\If {$T[m] > n$}
+			\State \Return $\mathrm{FindPos}(n, T, b, m)$
+		\Else
+			\State \Return $\mathrm{FindPos}(n, T, m+1, e)$
+		\EndIf
+	\EndIf
+\EndFunction
+	\\
+\Function{Sort}{$T$}
+	\State $n \gets \mathrm{size}(T)$
+	\State $S \gets [ T[0] ]$
+	\For{$i = 1$ \textbf{to} $n-1$}
+		\State $p \gets \mathrm{FindPos}(T[i], S, 0, \mathrm{size}(S))$
+		\State \textbf{insert} $T[i]$ \textbf{in} $S$ \textbf{at} $p$
+	\EndFor
+	\State \Return $S$
+\EndFunction
+\end{algorithmic}
+\caption{Binary insertion sort algorithm}
+\end{algorithm}
 
@@
 Sequence}, and is referenced under the name A001855.
+
+This sequence is linked to the construction of complete binary trees : $u_n$ is the sum of the depths of all nodes in the complete binary tree containing $n-1$ nodes (see \cite{btree}).
 
@@
 
-$n=2$ : $S_2(e_1) = (1,2)^{e_1}$
+$n=2$ : $C_2(e_1) = (1,2)^{e_1}$
 
-$n=3$ : $S_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$
+$n=3$ : $C_3(e_1,e_2,e_3) = (1,2)^{e_1} \circ (2,3)^{e_2} \circ (1,2)^{e_3}$
 
-$n=4$ : $S_4(e_1,e_2,e_3,e_4,e_5) = (1, 2)^{e_1} \circ (3,4)^{e_2} \circ
+$n=4$ : $C_4(e_1,e_2,e_3,e_4,e_5) = (1, 2)^{e_1} \circ (3,4)^{e_2} \circ
 (1,3)^{e_3} \circ (2, 4)^{e_4} \circ (1,2)^{e_5}$
@@
 
-$$S_2 = (1,2)$$
+$$C_2 = (1,2)$$
 
-$$S_3 = (1,2)(2,3)(1,2)$$
+$$C_3 = (1,2)(2,3)(1,2)$$
 
-$$S_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$
+$$C_4 = (1,2)(3,4)(1,3)(2,4)(1,2)$$
 
@@
 
-$$S_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$
+$$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$
 
@@
 \begin{aligned}
-    S_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
+    C_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
         & = & (0,1)(2,3)(4,5)(6,7) \\
@@
 
-For $n$ which is not a power of two, we construct $S_n^0$ by taking
-$S_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.
+For $n$ which is not a power of two, we construct $C_n^0$ by taking
+$C_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.
 
-For example, $S_5^0$ can be generated from $S_8^0$ and by removing quite a lot
+For example, $C_5^0$ can be generated from $C_8^0$ and by removing quite a lot
 of the boxes. We obtain the following solution :
 
-$$S_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$
+$$C_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$
 
@@
 
+\begin{thebibliography}{1}
+
+\bibitem{btree}Sung-Hyuk Cha, {\em On Integer Sequences Derived from Balanced k-ary Trees}, Applied Mathematics in Electrical and Computer Engineering, 2012.
+
+\end{thebibliography}
+
 \end{document}

### 2014-05-30 Article.tex
Changes..

@@
 $Card(\{0;1\}^{k}) \geq Card(\mathfrak{S}_n)$. We immediately obtain that $k$
-has to be greater than $\log_2(n!)$.\\ We also have an upper bound~: The
+has to be greater than $\log_2(n!)$.\\ We also have a reachable upper bound~: The
 traditional bubblesort gives a valid configuration of the SwitchBoxes problem. We
@@
 
-In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and
+In a second step, we show how we experimentally this conjecture for $n$ from 2 to 6, and
 how we demonstrated that the number of comparisons is an upper bound of the
@@
 $k$ given, creates all the possible configurations of $k$ boxes, and checks if
-one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,
+one of these configurations is valid. We first try it with $k = opt_{n-1}+1$. Then,
 we increment $k$ and try again until we get a valid configuration.  With this
@@
     \end{tabular}
-    \caption{Minimum box count for small number of wires}
+    \caption{Minimum box count for small number of wires, checked experimentally}
     \label{box-count}
@@
 
-\Large
 \begin{Conj*}
@@
 \end{Conj*}
-\normalsize
 

### 2014-05-30 Article.tex
Changes..

@@
 
-In a second step, we show how we experimentally this conjecture for $n$ from 2 to 6, and
+In a second step, we show how we experimentally checked this conjecture for $n$ from 2 to 6, and
 how we demonstrated that the number of comparisons is an upper bound of the

### 2014-05-30 Article.tex
Changes..
...

--- 2014-05-30 Article.tex
@@
 
-\subsection{Truncation}
+\subsection{Downscaling}
 
 For $n$ which is not a power of two, we construct $C_n^0$ by taking
-$C_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.
+$C_{2^{\ceil{log_2(n)}}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.
 
-For example, $C_5^0$ can be generated from $C_8^0$ and by removing quite a lot
-of the boxes. We obtain the following solution :
+For example, $C_5^0$ can be generated from $C_8^0$ and by removing 11 of the 20
+boxes. We obtain the following solution :
 
@@
 
-For a box system $S = b_1 b_2 \dots b_p$, we construct the sets :
+For a box system $C = b_1 b_2 \dots b_p$, we construct the sets :
+
+$$Perm_k = (b_1 b_2 \dots b_k)(\left\{0,1\right\}^k)$$
+
+These sets are recursively defined by :
 
 $$Perm_0 = { id }$$
-$$Perm_k = (b_1 b_2 \dots b_k)(\left\{0,1\right\}^k)$$
+$$Perm_{k+1} = Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
+\right\}$$
 
@@
 permutations of $\mathfrak{S}_n$ and the numbers $\left\{0,1,\dots,n!-1\right\}$ is
-constructed using the standard method described in (a citation).
+constructed using the standard Lehmer code.
 
@@
 
-We can easily detect that $Perm_{k+1} = Perm_k$ when $ \# Perm_{k+1} = \# Perm_k$,
+We can easily detect that $Perm_{k+1} = Perm_k$ when $ |Perm_{k+1}| = |Perm_k|$,
 because $Perm_k \subset Perm_{k+1}$. When this condition is fulfilled, then we
@@
 generate all the permutations for $n \leq 13$ and that have $u_n$ boxes (ie the
-conjectured optimum). We have not managed to run the test for $n \geq 14$,
-because the required RAM exceeds 20Go, which is not a resource we have in our
-possession.
+conjectured optimum). We note the simplified system for $n$ wires $C_n^1$. We
+have not managed to run the test for $n \geq 14$, because the required RAM
+exceeds 20Go, which is not a resource we have in our possession.
+
+For example for $n=5$, we have :
+
+$$C_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$
+$$C_5^1 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(0,1)(2,3)$$
+
+\begin{figure}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Number of wires $n$ & Size of $C_n^0$ & Size of $C_n^1$ & $opt_n$ &
+	$u_n$ \\
+    \hline
+    2 & 1 & 1 & 1 & 1 \\
+    3 & 3 & 3 & 3 & 3 \\
+    4 & 6 & 5 & 5 & 5\\
+    5 & 9 & 8 & 8 & 8\\
+    6 & 12 & 11 & 11 & 11 \\
+    7 & 15 & 14 &   & 14\\
+    8 & 20 & 17 &   & 17\\
+    9 & 25 & 21 &   & 21\\
+    10 & 28 & 25 &   & 25\\
+    11 & 31 & 29 &   & 29\\
+    12 & 34 & 33 &   & 33\\
+    13 & 39 & 37 &   & 37\\
+    \hline
+    \end{tabular}
+    \caption{Minimum box count for small number of wires, checked experimentally}
+    \label{box-count}
+\end{figure}
 
@@
 
-All these results seem to confirm our intuition.
-To go further, we unsuccessfully tried to find applications from the set of trees representing a sort by binary insertion to the set of valid configurations of boxes 
-that would be either one to one or onto, in order to find an inequality between these two sequences of integers.
-We also tried to put our construction of configurations in relation with binary insertion sort.
+All these results seem to confirm our intuition.  To go further, we
+unsuccessfully tried to find applications from the set of trees representing a
+sort by binary insertion to the set of valid configurations of boxes that would
+be either one to one or onto, in order to find an inequality between these two
+sequences of integers.  We also tried to put our construction of configurations
+in relation with binary insertion sort.
 

### 2014-05-30 Article.tex

@@
 }
+\newcommand{\comp}{\operatornamewithlimits{\bigcirc}}
 
@@
 \newtheorem*{Conj*}{Conjecture}
+\newtheorem*{def*}{Définition}
 
@@
 
-In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and
+In a second step, we show how we experimentally checked this conjecture for $n$ from 2 to 6, and
 how we demonstrated that the number of comparisons is an upper bound of the
@@
 
-We first define the $q$-block at position $i$ by :
+We first define $B(q,i)$, the $q$-block at position $i$ by :
 
-$$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1)(q+2*2^i-1)$$
+\begin{def*}
+$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) = \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)$
+\end{def*}
+For example: 
+$$B(q,0) = (q,q+1)$$
+$$B(q,1) = (q, q+2)(q+1, q+3)$$
+$$B(q,2) = (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)$$
 
-For example: 
-$$B(0,i) = (i,i+1)$$
-$$B(1,i) = (i, i+2)(i+1, i+3)$$
-$$B(2, i) = (i,i+4)(i+1,i+5)(i+2,i+6)(i+3,i+7)$$
+Then, for $n=2^p$ we define $L(p,q)$, for $q < p$ the $(p,q)$-line by :
 
-Then, for $n=2^p$ we define for $q < p$ the $(p,q)$-line by :
-
-$$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$$
+\begin{def*}
+$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$
+\end{def*}
 
@@
 
-$$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$
+\begin{def*}
+$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$
+\end{def*}
 
@@
 \end{figure}
+
+\begin{Conj*}
+$C_n^0$ generates all permutations fon $n$
+\end{Conj*}
 

### 2014-05-30 Article.tex
Changes..
Equation alignment
Add figures

@@
 
+\usepackage{color}
 \usepackage[utf8]{inputenc}
@@
 
+\begin{figure}
+ \centering
+ \begin{minipage}{.5\textwidth}
+    \centering
+     \def\svgwidth{0.5\textwidth}
+     \includesvg{svg/box0}
+     \caption{A switch box with control bit not set}
+ \end{minipage}%
+ \begin{minipage}{.5\textwidth}
+    \centering
+     \def\svgwidth{0.5\textwidth}
+     \includesvg{svg/box1}
+     \caption{A switch box with control bit set}
+ \end{minipage}
+\end{figure}
+
 Given this problem, we tried to determine the best lower bound of the number of
@@
 $S$ at a position calculated by the $FindPos$ function. The $FindPos$ function
-is based on a binary search, therefore does $O(log(S.size))$ comparisons.
+is based on a binary search, therefore does $O(log(\mathrm{size}(S)))$ comparisons.
 
@@
 
-$$u_1 = 0$$
-$$\forall n \in \mathbb{N}^*, u_{n+1} = u_n + \ceil{log_2(n)}$$
+$$\begin{array}{r l l}
+	u_1 &=& 0 \\
+    \forall n \in \mathbb{N}^*, u_{n+1} &=& u_n + \ceil{log_2(n)}
+\end{array}$$
 
@@
 Hence, we have $opt_3=3$.
-
-\begin{figure}
-    \centering
-    \def\svgwidth{0.7\textwidth}
-    \includesvg{svg/boxsys-8-20}
-    \caption{Simple non-optimal solution for 8 wires}
-\end{figure}
 
@@
 \begin{def*}
-$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) = \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)$
+$$\begin{array}{l l l}
+	B(q,i) & = & (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) \\ & & \\
+		   & = & \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)
+	\end{array}$$
 \end{def*}
+
 For example: 
-$$B(q,0) = (q,q+1)$$
-$$B(q,1) = (q, q+2)(q+1, q+3)$$
-$$B(q,2) = (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)$$
+$$\begin{array}{l l l}
+	B(q,0) &=& (q,q+1) \\
+	B(q,1) &=& (q, q+2)(q+1, q+3) \\
+	B(q,2) &=& (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)
+\end{array}$$
 
@@
 \end{def*}
+
+A line is just the union of disjoint blocks of same size, so that all the wires are used by the blocks.
 
@@
 $$
-\begin{aligned}
+\begin{array}{l l l}
     C_8^0 & = & L(3,0) L(3,1) L(3,2) L(3,1) L(3,0) \\
@@
         & & (0,1)(2,3)(4,5)(6,7)
-\end{aligned}$$
+\end{array}$$
+
+\begin{figure}
+    \centering
+    \def\svgwidth{0.7\textwidth}
+    \includesvg{svg/boxsys-8-20}
+    \caption{Representation of $C_8^0$}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \def\svgwidth{0.9\textwidth}
+    \includesvg{svg/intuition}
+    \caption{Explanation of our intuition leading to the construction of $C_{2^j}^0$}
+\end{figure}
 
@@
         \includesvg{svg/boxsys-5-9}
-        \caption{Solution for 5 wires}
+        \caption{Solution for 5 wires: $C_5^0$}
     \end{minipage}%
@@
         \includesvg{svg/boxsys-6-12}
-        \caption{Solution for 6 wires}
+        \caption{Solution for 6 wires: $C_6^0$}
     \end{minipage}
@@
 
-$$Perm_0 = { id }$$
-$$Perm_{k+1} = Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
-\right\}$$
+$$\begin{array}{l l l}
+	Perm_0 &=& { id } \\
+	Perm_{k+1} &=& Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
+\right\} 
+\end{array}$$
 

### 2014-06-01 Article.tex
Translate intuition ; integrate to article.

@@
 
+\subsection{Explaining our intuition}
+
+We work here with $n = 2^p$ wires. Our idea is that we need to be able to route
+any of the $n$ input wires to any of the $n$ output wires. A box enables the
+{\em swapping} or {\em non-swapping} of two wires. Its behaviour is tightly
+linked with that of the two wires.
+
+We tried to imagine a step of {\em multiplexing} followed by a step of {\em
+demultiplexing}, that would regroup all the wires in one point before deciding
+which wire goes where. Since one box is plugged on two wires, we can imagine its
+output as being one bus of two wires. The idea is thus relatively simple :
+
+\begin{itemize}
+	\item We begin with $n = 2^p$ simple wires
+	\item We group them two by two into $2^{p-1}$ buses of size $2$
+	\item We group the buses two by two into $2^{p-1}$ buses of size $4$
+	\item \dots
+	\item We group the two buses of size $2^{p-1}$ into one bus of size $2^p$.
+\end{itemize}
+
+Now the demultiplexing step is just the opposite :
+
+\begin{itemize}
+	\item We begin with one bus of $2^p$ wires that we separate into two smaller
+	buses of $2^{p-1}$ wires
+	\item \dots
+	\item We separate the $2^{p-1}$ buses of 2 wires into $2^p$ simple wires.
+\end{itemize}
+
+The grouping/separation of wires requires a given number of boxes, and we tried
+to put just that number of boxes in the box system we designed. Grouping two
+buses of $k$ wires requires $k$ boxes.
+
+\begin{figure}
+    \centering
+    \def\svgwidth{0.9\textwidth}
+    \includesvg{svg/intuition}
+    \caption{Explanation of our intuition leading to the construction of $C_{2^j}^0$}
+\end{figure}
+
+We tried this box system and found, for small values of $n$, that it worked.
+
+\subsubsection{Number of boxes}
+
+Let $n = 2^p$ be the number of wires. On each line of grouping/separating we
+have $n/2$ boxes. We now need to count lines of grouping and of separating. We
+begin from $n=2^p$ wires and want to group them into 1 bus, therefore we need
+$p$ lines of grouping. Conversely, we then need to separate one bus into $2^p$
+wires, therefore requiring $p$ lines of separating.
+
+We notice that the last line of grouping and the first line of separating have
+exactly the same boxes and each wires is used by exactly one grouping box and
+one separating box. These two lines are thus redundant and we only put one of
+them.
+
+Finally :
+
+$$\begin{array}{l l l}
+	\# \mathrm{boxes} &=& \# \mathrm{boxes per line} \times \left(
+			\# \mathrm{group lines} + \# \mathrm{separate lines} - 1
+			\right) \\
+		&=& \frac{n}{2} (2 p - 1) \\
+		&=& n ^ {p - 1/2} \\
+		&=& n ^ {log_2 n - 1/2}
+\end{array}$$
+
 \subsection{The basis box configuration}
@@
     \caption{Representation of $C_8^0$}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \def\svgwidth{0.9\textwidth}
-    \includesvg{svg/intuition}
-    \caption{Explanation of our intuition leading to the construction of $C_{2^j}^0$}
 \end{figure}
